---
title: "Stegastes fuscus behavior"
date: "2023-03-02"
output: github_document
---

Behavior of *Stegastes fuscus* in three different reef sites found around the CEBIMar, São Sebastião, São Paulo, BR.
We tested whether the relationship between # chases and # bites differed between adults and subadults, and whether the transitions between these behaviors changed across sites.


<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
<!-- badges: end -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We ran two state-space models to estimate the transition rates between the following levels: model 1: probability of keep biting (parameter phi), probability of shift from chase to bite (parameter gamma); model 2: probability of keep chasing (phi), and probability of shift from bite to chase (phi). PS: The correct model would be a multi-state model where all these probabilities could be estimated in one unique model (had no time to implement it).
Each model has the following structure:

```{r comment='', echo = F}
cat(readLines('Model_dyn.txt'), sep = '\n')
```

And the resulting transition rates between behavioral states (chase and bites) were:

```{r, echo = F, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="80%",out.height="80%",results='hide'}

source ("R/script.R")


a



```

Useful summary statistics

```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


summary_stats



```


Relationship between foraging (bites) and persecution (chases) rates, for adult and subadult damsel fish.

```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


plot_cor



```


The composition of chased species 

```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


plot_freq_chased



```


<!-- badges: start -->
<!-- badges: end -->


#### These results were produced using the following software and associated packages:

```{r pressure, echo=F,warning=F,message=F}

sessionInfo()


```
