---
title: "Stegastes fuscus behavior"
date: "2023-03-02"
output: github_document
---

Behavior of *Stegastes fuscus* in three different reef sites found around the CEBIMar, São Sebastião, São Paulo, BR.
We tested whether the relationship between # chases and # bites differed between adults and subadults, and whether the transitions between these behaviors changed across sites.


<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
<!-- badges: end -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We ran two state-space models to estimate the transition rates between the following levels: model 1: probability of keep biting (parameter phi), probability of shift from chase to bite (parameter gamma); model 2: probability of keep chasing (phi), and probability of shift from bite to chase (phi). PS: The correct model would be a multi-state model where all these probabilities could be estimated in one unique model (had no time to implement it).

You need to install the software "JAGS" to run these analyses. Find the link here [https://sourceforge.net/projects/mcmc-jags/].


Each model has the following structure:

```{r comment='', echo = F}
cat(readLines('Model_dyn.txt'), sep = '\n')
```


And the resulting transition rates between behavioral states (chase and bites) were:
- transitions of states - ages
```{r, echo = F, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="80%",out.height="80%",results='hide'}

source ("R/script.R")


a



```

Average rates
```{r, echo = F, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="80%",out.height="80%",results='hide'}

mcmc_res_av[,c(1,3,7)]


```

- transitions of states - sites
```{r, echo = F, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="80%",out.height="80%",results='hide'}


a_sites




```

Averaged rates
```{r, echo = F, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="80%",out.height="80%",results='hide'}


mcmc_res_av_sites[,c(1,3,7)]



```

Useful summary statistics

```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


summary_stats



```


Analysis of variance

No difference of # bites among sites and ages
```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


summary(aov (formula = sum_count~ age*site,
       data=data_anova_bites))

```


Higher number of chases among subadults
```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


# no effect of site and age on bite rates 
summary(aov (formula = sum_count~ age*site,
             data=data_anova_chase))


plot_anova

```


Relationship between foraging (bites) and persecution (chases) rates, for adult and subadult damsel fish.

```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


plot_cor



```


The composition of chased species 

```{r, echo = T, fig.height=5,fig.width=6,fig.align= "center",fig.margin=T, message=F, warning=F,out.width="70%",out.height="70%",results='hide'}


plot_freq_chased



```


<!-- badges: start -->
<!-- badges: end -->


#### These results were produced using the following software and associated packages:

```{r pressure, echo=F,warning=F,message=F}

sessionInfo()


```
